---
title: "exercise-04"
format: html
editor: visual
---

### step 1

create a function that loads in a dictionary that loads in a data set takes in file name.

```{r}
library(dplyr)
library(stringr)

load_dictionary <- function(filename) {
  words <- read.delim(filename, header = FALSE, stringsAsFactors = FALSE)$V1
  return(words)
}
```

```{r}
c <-"https://raw.githubusercontent.com/difiore/ada-datasets/refs/heads/main/collins-scrabble-words-2019.txt"
g<-"https://raw.githubusercontent.com/difiore/ada-datasets/refs/heads/main/google-10000-english-usa-no-swears.txt"
```

```{r}
solution_list <-load_dictionary(g)
valid_list<-load_dictionary(c)
```

Testing the code so far..

```{r}
str(valid_list)
```

```{r}
str(solution_list)
```

```{r}
solution_list <- intersect(solution_list, valid_list)
```

```{r}
print(length(solution_list))
```

Above, we winnowed the solution_list variable and found that the new list contains 8337 words

Next, we remove all words that are not 5 letters long, and randomly select one of those remaining 5 letter words as the solution

```{r}
pick_solution <- function(solution_list) {
  solution_list <- solution_list[nchar(solution_list) == 5]
  solution_word <- sample(solution_list, 1)
  wordvec <- strsplit(solution_word, "")[[1]]
  
  return(wordvec)
}
```

```{r}
wordvec <- pick_solution(solution_list)
```

```{r}
wordvec
```

Now to put the game together using a function "play_wordle", first writing a code for how the function will evaluate the variables associated with the user guess.

```{r}
play_wordle <- function(wordvec) {
  cat("Welcome to Wordle by Megan and Erika!\n")
  cat("You have six guesses to get the 5-letter word. Good luck!\n\n")
  
  guesses_left <- 6
  letters_left <- LETTERS
  
  while (guesses_left > 0) {
    cat("Letters left:", paste(letters_left, collapse = " "), "\n")
    guess <- readline(paste0("Enter guess (", guesses_left, " left): "))
    
    guess <- toupper(guess)
    while (nchar(guess) != length(wordvec)) {
      guess <- readline("Invalid input! Enter a 5-letter word: ")
      guess <- toupper(guess)
    }
    
    result <- evaluateGuess(guess, wordvec)
    cat("Result: ", paste(result, collapse = " "), "\n\n")

    letters_left <- setdiff(letters_left, unlist(strsplit(guess, "")))
    
    if (all(result == "G")) {
      cat("You won in", 7 - guesses_left, "guesses!\n")
      return()
    }
    
    guesses_left <- guesses_left - 1
  }
  
  cat("Sorry, you lost! The word was:", paste(wordvec, collapse = ""), "\n")
}
```
